Reasoning Graphically about Quantum Computation

### 2008-02-24 papers/reasoning-graphically/paper.tex
trivial test change
git-svn-id: https://isaplanner.svn.sourceforge.net/svnroot/isaplanner/trunk/quantomatic@1350 f8f375fb-4f10-0410-8d47-b6fbdc7ca053
um this is an accident... you probably want to ignore
git-svn-id: https://isaplanner.svn.sourceforge.net/svnroot/isaplanner/trunk/quantomatic@1351 f8f375fb-4f10-0410-8d47-b6fbdc7ca053
some restructuring.
git-svn-id: https://isaplanner.svn.sourceforge.net/svnroot/isaplanner/trunk/quantomatic@1352 f8f375fb-4f10-0410-8d47-b6fbdc7ca053

\section{Compact Categories and Graphs}
\label{sec:mono-categ-graphs}

\section{Representation and Compositionality}
\label{sec:repr-comp}

\section{Graph Patterns and Matching}
\label{sec:graph-patt-match}

>>>>

\section{Compact Closed Categories and Graphs}
\label{sec:mono-categ-graphs}

\section{Graph Patterns}
\label{sec:patterns}

The representation of Compact Closed Categories as Graphs, discuseed
in the previous section, is too restrictive for automated reasoning
about quantum computation. In particular, pictures such as the
following are frequently needed:

\begin{center}
  \scalebox{1.0}{\includegraphics{images/spider_lhs.eps}}
\end{center}

\noindent Such pictures represent an infinite family of concrete
graphs. In this section we describe an extension of the representation
for Compact Closed Categories that allows a graph-based representation
that captures an infinite family of graphs. Notably, this allows us to
represent laws about quantum computation, such as
Spider-Law~\ref{spider-law-fig}. Furthermore, this representation is
still compositional in the sense that we can compose graphs. The
extension, which we call \ref{graph patterns}, adds two extra kinds of
nodes to the graph: {\em banged nodes} which informally represent an
arbitrary number of copies of that node, and {\em variable nodes}
which informally represent some as yet unkown node in a graph.

\subsection{Banged Nodes}

\subsection{Variable Nodes}

\subsection{Compositonality}

\section{Graph Rewriting}
\label{sec:rewriting}

\subsection{Rules}
\subsection{Matching}
\subsection{Substitution}

\section{Related Work}
\label{sec:relatedwork}
